%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Head of AI Engineering} % Job title
    {\href{https://tymit.com}{Tymit}} % Organization
    {Dubai (United Arab Emirates)} % Location
    {July 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] Leading Tymit's AI Engineering practice across customer-facing AI products and internal AI tooling. Setting technical direction and staying hands-on in architecture and code for the most critical flows; partner with Product, Data, Commercial and the exec team on the AI strategy.
        \item[]
        \item[] Shipped customer-facing multi-agent systems in the Tymit product, powering self-service and in-app decisioning, with end-to-end evaluation, tracing and regression testing before every production rollout.
        \item[]
        \item[] Designing and building a proprietary Agentic Memory manager to tackle one of the hardest problems in production agents: context management across long-running, multi-turn and multi-agent conversations. The system coordinates short-term working memory with long-term episodic and semantic memory, and assembles retrieval-augmented context within strict token budgets — keeping agents coherent across sessions without blowing cost or latency.
        \item[]
        \item[] Built internal developer-experience agents that automate repetitive work across the SDLC, measurably reducing time-to-market and freeing engineers for higher-leverage work.
        \item[]
        \item[] Drove the agentisation of internal operations — replacing manual workflows in Support, Ops and Engineering with agents integrated into existing systems.
        \item[]
        \item[] Own the AI technical roadmap end-to-end: foundation-model evaluation and routing, orchestration stack, guardrails, evals and observability, and the AI Engineering hiring plan.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {B2B Engineering Lead} % Job title
    {\href{https://tymit.com}{Tymit}} % Organization
    {Dubai (United Arab Emirates)} % Location
    {January 2024 - July 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] Owned end-to-end delivery of technical integrations with strategic B2B partners, aligning engineering execution with commercial and product goals.
        \item[]
        \item[] Designed secure API and microservices architecture for partner integrations, with a focus on scalability, observability and compliance.
        \item[]
        \item[] Led and mentored the integrations engineering team; set delivery processes, technical standards and the review culture.
        \item[]
        \item[] Worked cross-functionally with Product, Commercial and external partners to unblock integrations and close partner launches.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Director of Engineering} % Job title
    {\href{https://getbaraka.com}{Baraka (YC S21)}} % Organization
    {Dubai (United Arab Emirates)} % Location
    {October 2022 - January 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] Led an engineering organisation of 25 engineers across Back-end, Mobile, Web, DevOps and QA, reporting directly to the founding team (CEO and CTO).
        \item[]
        \item[] Owned architecture for the trading platform with a focus on high-availability, low-latency, and security — aligned with regulatory requirements.
        \item[]
        \item[] Scaled the engineering organisation through hiring, mentoring and training programmes; introduced technical career paths and a structured review process.
        \item[]
        \item[] Worked closely with the ExCo team on product positioning and revenue-generating initiatives, translating business needs into technical capabilities.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Lead} % Job title
    {\href{https://wio.io}{Wio Bank}} % Organization
    {Abu Dhabi (United Arab Emirates)} % Location
    {May 2022 - October 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] Built Wio Bank's lending platform from scratch, leading a team of 10 engineers (Back-end, Front-end, DevOps and QA).
        \item[]
        \item[] Defined the MVP scope and platform architecture in close collaboration with stakeholders; hired the team and set engineering processes.
        \item[]
        \item[] Managed partner relationships and owned technical conversations with third-party providers.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineering Lead} % Job title
    {\href{https://tymit.com}{Tymit}} % Organization
    {London (United Kingdom)} % Location
    {March 2021 - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] Promoted into the Lead role. Managed an engineering team of 15 engineers and owned backend architecture for scalable, reliable and secure systems.
        \item[]
        \item[] Partnered with stakeholders and Product on the company roadmap and technical decision-making.
        \item[]
        \item[] Kept hands-on contribution on customer-facing features alongside the leadership responsibilities.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Software Engineer} % Job title
    {\href{https://tymit.com}{Tymit}} % Organization
    {London (United Kingdom)} % Location
    {February 2018 - March 2021} % Date(s)
    {
      \begin{cvitems}% Description(s) of tasks/responsibilities
        \item[]\textbf{Employee no. 1}.
        \item[]
        \item[] Built the initial product from scratch as a monolith to reach an early MVP. After \textasciitilde1 year, led the migration to a microservices architecture to support company scale and clearer domain boundaries.
        \item[]
        \item[] Contributed to business decisions alongside stakeholders and shipped core customer-facing capabilities end-to-end.
        \item[]
        \item[] Mentored incoming engineers and owned technical onboarding as the team grew.
        \item[]
        \item[] Key customer features shipped:
        \item[]
        \item {Wallets integration (Apple Pay \& Google Pay) }
        \item {Open Banking: Payment Initiation Services (PIS) \& Account Information Services (AIS) }
        \item {Direct Debit}
        \item {Real-time authorisations / transactions / payments, 3D Secure}
        \item {KYC}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Associate Lecturer} % Job title
    {\href{https://www.urjc.es}{Universidad Rey Juan Carlos}} % Organization
    {Madrid (Spain)} % Location
    {January 2019 - August 2021} % Date(s)
    {
      \begin{cvitems}% Description(s) of tasks/responsibilities
        \item[] Associate Lecturer in the \href{https://gestion2.urjc.es/pdi/departamento/Y157}{Department of Computing Science, Computer Architecture, Programming Languages and Systems and Statistics and Operative Investigation}.
        \item[]
        \item[] Taught the following subjects:
        \item[]
        \item {High Performance Computing}
        \item {Distributed Systems}
        \item {Mobile Application Development}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Senior Software Engineer} % Job title
    {\href{https://www.santander.co.uk}{Santander UK}} % Organization
    {Milton Keynes (United Kingdom)} % Location
    {September 2017 - February 2018} % Date(s)
    {
      \begin{cvitems}% Description(s) of tasks/responsibilities
        \item[] R\&D department — several innovation projects:
        \item[]
        \item {Implemented a Blockchain solution for an internal project}
        \item {Led the OCR project for identity document verification}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Senior Software Engineer} % Job title
    {\href{https://babel.es/en}{BABEL}} % Organization
    {Madrid (Spain)} % Location
    {October 2015 - September 2017} % Date(s)
    {
      \begin{cvitems}% Description(s) of tasks/responsibilities
        \item[] IT consulting firm — delivered projects for \textbf{BBVA}, \textbf{Orange}, \textbf{Telefónica}, \textbf{Sanitas} and \textbf{HM Hospitales}, among others.
        \item[]
        \item[] Mostly as individual contributor; also led teams of 5-6 engineers using agile methodologies, supporting on technical design and reviews.
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Junior Software Engineer} % Job title
    {\href{http://www.grupocomunica.com/}{Grupo Comunica}} % Organization
    {Córdoba (Spain)} % Location
    {May 2013 - September 2014} % Date(s)
    {
      \begin{cvitems}% Description(s) of tasks/responsibilities
        \item {Developed Android \& iOS applications}
        \item {Built an audio-visual streaming project}
      \end{cvitems}
    }

\end{cventries}
